More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
notations in weak + ref a forte
coorection and explanations of Fig3/example1

Fig. \ref{ABP:Schema} shows the example principle: two unspecified
processes $P$ and $Q$ (Holes) communicate messages, with a data value
argument, through the two protocol entities $sender$ and
$receiver$. The underlying unsafe network is modelled by two media,
carrying the message together with a control bit on one way, and an
acknowledge back form $Q$ to $P$. The media can be perfect (safe), or
faulty (losing or duplicating messages) as shown in
Fig. \ref{schema:ABP-media}.

@@

\TODO{Add somewhere a subsection ``running example'' ?}

%%\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $m,b$ to the medium) is:

@@

At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has a subnet. One of its possible transition (synchronizing the hole $P$ with the $Protocol$) is:
 \smallskip
 $  OT_1  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
%                            \xrightarrow{in(?m,?b)}_{M1}
      \{\xrightarrow{send(m)}_P\}; Pred=True; Post=\{s1\_m:=m\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {ABP_1 \OTarrow{\underline{send(m)}} ABP_2}
  $
\end{example}

>>>>

Fig. \ref{ABP:Schema} shows the example principle: two unspecified
processes $P$ and $Q$ (Holes) communicate messages, with a data value
argument, through the two protocol entities $sender$ and
$receiver$. The underlying network is modelled by two media,
carrying the message together with a control bit on one way, and an
acknowledge back form $Q$ to $P$. The media can be perfect (safe), or
faulty (losing or duplicating messages) as shown in
Fig. \ref{schema:ABP-media}.

@@

%\TODO{Add somewhere a subsection ``running example'' ?}

%%\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:

@@

    \smallskip
    Here the global states $Prot_1$ and $Prot_2$ encode the states of
    the 4 pLTS composing the system, namely
    $Prot_1=\ostate{s_1,m_0,m_0,r_0}$ and
    $Prot_2=\ostate{s_2,m_1,m_0,r_0}$, showing that the sender and the
    first medium have evolved during this transition.
    The predicate $Pred$ involves the state variables $s_1\_m$ and
    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
    state variables of the medium.

    \smallskip
At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
a subnet. One of its possible transition (synchronizing the hole $P$
with the $Protocol$) is:

 \smallskip
 $  OT_1  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
%                            \xrightarrow{in(?m,?b)}_{M1}
      \{\xrightarrow{send(m)}_P\}; Pred=True; Post=\{s1\_m:=m\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {ABP_1 \OTarrow{\underline{send(m)}} ABP_2}
    $

    \smallskip
    The global states $ABP_1$ and $ABP_2$ have the same structure than
    $Prot_1$ and $Prot_2$, as the holes have no states. The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.
\end{example}
